\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-10 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/robust_hhi.tex 	modified:   result_tables/robust_mature.tex 	modified:   result_tables/stylized_fact.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters in the Age of Platforms: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed. Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market. We can denote the number of two types of brokerages by $B_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{B_{i, i}}{B_{i, 1} + B_{i, 2}}$. We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.

The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{j}^2} > 0$ where $j \in \{1, 2\}$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.

We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}. Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and $L^B_i$ broad searchers that are searching for all the communities in the market.

We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by

\begin{equation}
  N_i = L^N_i \times \frac{B_{i, j}}{B_{i, 1} + B_{i, 2}}. \label{eq:naive_prob}
\end{equation}

However, the broad searchers in the market are attracted to the platform by the

>>>>

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters in the Age of Platforms: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed. Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market. We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$. We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$. % we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.

The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2\}$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.

We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}. Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria. When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints. Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$.

We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by the proportion of number of houses listed in the brokerage $j$ and the total number of houses listed in the community $i$:

\begin{equation}
  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}. \label{eq:naive_prob}
\end{equation}

However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market,

\begin{equation}
  B_i = L^B_i \times \alpha_j \frac{\mathcal{B}_{i, j}}{\sum_{i^\prime \neq i} (\mathcal{B}_{i^\prime, 1} + \mathcal{B}_{i^\prime, 2})} \label{eq:broad_prob}
\end{equation}
